### 2020-01-22 defesa/tex/chapter/mcer.tex
wip

\begin{teorema}
	Let $(\Pp, \Ww, \Rr)$ be an instance of MCER, and $\Omega(\Pp, \Ww, \Rr)$ be a set of solutions defined by \autoref{eq:omega}. Then there exists an optimal solution $(Q^*, \Theta^*) \in \Omega(\Pp, \Ww, \Rr)$, and $|\Omega(\Pp, \Ww, \Rr)|=\bigO(n^{3m})$.	
\end{teorema}
\begin{proof}
	For every $j \in \{1, \dots, m\}$, by \autoref{lema:3pnts}, any optimal solution that covers more than one point can be transformed into one that is in $S_j^{(2)}$ or in $S_j^{(3)}$.
	If an optimal solution covers only one point, it can be transformed into another one that is in $S_j^{(1)}$.

@@

>>>>

\begin{theorem}\label{th:mcer}
	Let $(\Pp, \Ww, \Rr)$ be an instance of MCER, and $\Omega(\Pp, \Ww, \Rr)$ be a set of solutions defined by \autoref{eq:omega}. Then there exists an optimal solution $(Q^*, \Theta^*) \in \Omega(\Pp, \Ww, \Rr)$, and $|\Omega(\Pp, \Ww, \Rr)|=\bigO(n^{3m})$.	
\end{theorem}

\begin{proof}
	For every $j \in \{1, \dots, m\}$, by \autoref{lema:3pnts}, any optimal solution that covers more than one point can be transformed into one that is in $S_j^{(2)}$ or in $S_j^{(3)}$.
	If an optimal solution covers only one point, it can be transformed into another one that is in $S_j^{(1)}$.

@@

In this section we describe an algorithm for MCER that simply goes through every solution in $\Omega(\Pp, \Ww, \Rr)$ and therefore finds an optimal solution.

Firstly, we describe an algorithm that returns a CLS for an ellipse given a demand set. 
We assume that in \autoref{algoritmo:mcer1} the procedure $e2p(u, v, a, b)$ returns every $(q, \theta) \in \R^2\times\R$, such that, let $E$ be the coverage region of the ellipse with shape parameters $(a, b)$, $\{u, v\}\subset \partial E(q, \theta)$, and
$\theta$ is an rotation angle that makes $E$'s major-axis parallel to the line defined by $u$ and $v$.

\begin{algoritmo}
	\caption{Algorithm for MCER}\label{algoritmo:mcer1}
	\begin{algorithmic}[1]
		\Require{A set of points $\Pp=\{p_1,\dots,p_n\}$, and an ellipse's shape parameters $(a, b)$.}

		\Ensure{A CLS for the ellipse with shape parameters $(a, b)$ considering the demand set $\Pp$.}

		\item[]

		\Procedure{$MCER_1$}{$\Pp, a, b$}
		\State $S \gets \{\}$

		\For {$u \in \Pp$}
		\State $S \gets S \cup \{(u, 0)\}$
		\EndFor

		\For {$\{u, v\} \in \Pp$}
		\State $S \gets S \cup e2p(u, v, a, b)$
		\EndFor

		\For{$\{u, v, w\} \in \Pp$}
		\State $S \gets S \cup e3p(u, v, a, b)$ \Comment{Defined in \autoref{algoritmo:e3p}.}
		\EndFor

		\State \Return $S$
		\EndProcedure
	\end{algorithmic}
\end{algoritmo}

After that, we define \autoref{algoritmo:mcer} which takes an instance $(\Pp, \Ww, \Rr)$ of MCER, and returns an optimal solution for it.

\begin{algoritmo}
	\caption{Algorithm for MCER}\label{algoritmo:mcer}
	\begin{algorithmic}[1]
		\Require{A set of points $\Pp=\{p_1,\dots,p_n\}$, a list of weights $\Ww=\{w_1, \dots, w_n\}$, and a list of shape parameters $\Rr=\{(a_1, b_1), \dots, (a_m, b_m)\}$.}

		\Ensure{An optimal solution of MCER.}

		\item[]

		\Procedure{$MCER$}{$\Pp, \Ww, \Rr, j=1$}
		\If{$j = m+1$}
		\State \Return $0$
		\EndIf

		\State $ans \gets 0$
		\State Let $(q_{j}^*, \dots, q_m^*); (\theta_{j}^*, \dots, \theta_m^*)$ be the optimal solution, initially set to $0$.

		\State $S_j \gets MCE_1(\Pp, a_j, b_j)$

		\For{$(q_j, \theta_j) \in S_j$}
		\State $Cov \gets \Pp \cap E_j(q_j, \theta_j)$
%		\State $((q_{j+1},\theta_{j+1}); \dots; (q_m, \theta_m)) \gets  MCE(\Pp\setminus Cov, \Ww, \Rr, j+1)\}$

		\State $(q_{j+1}, \dots, q_m); (\theta_{j+1}, \dots, \theta_m) \gets  MCE(\Pp\setminus Cov, \Ww, \Rr, j+1)$

		\State $Cov \gets \bigcup_{k=j}^m \Pp \cap E_k(q_k, \theta_k)$
		\If {$w(Cov) > ans$}
			\State $ans \gets w(Cov)$
			%\State $((q_{j}^*,\theta_{j}^*); \dots; (q_m^*, \theta_m^*)) \gets ((q_{j},\theta_{j}); \dots; (q_m, \theta_m))$

			\State $(q_{j}^*, \dots, q_m^*); (\theta_{j}^*, \dots, \theta_m^*) \gets (q_{j}, \dots, q_m); (\theta_{j}, \dots, \theta_m)$
		\EndIf
		\EndFor

		\State \Return $(q_{j}^*, \dots, q_m^*); (\theta_{j}^*, \dots, \theta_m^*)$
		\EndProcedure
	\end{algorithmic}
\end{algoritmo}

\begin{corolario}
	\autoref{algoritmo:mcer} takes $\bigO(n^{3m})$ computations and returns an optimal solution.
\end{corolario}

\begin{proof}
	For every $j\in\{1, \dots, m\}$, let $Z \subset \Pp$ be the set of covered points by ellipses $1, \dots, j-1$. 
	Unless $Z=\Pp$, \autoref{algoritmo:mcer} does not go through a solution that has $(q_j, \theta_j)$, such that $\Pp \cap E_j(q_j, \theta_j) \subset Z$. Apart from those solutions, which are non-optimal, \autoref{algoritmo:mcer} considers every solution in $\Omega(\Pp, \Ww, \Rr)$.
\end{proof}

\subsection{Improvements and implementation details}

Some improvements can be made when implementing \autoref{algoritmo:mcer}.
